Untitled

### 2021-01-27 ms/manuscript.Rmd
Add timescale to tree

```{r combined-plot, fig.width = 6.85, fig.height = 5, fig.cap = ""}
# Copy phylogeny and species means data so they
# can be manipulated for this plot
phy <- filmy_phy
traits <- combined_species_means

@@

filmy_habit <-
  filmy_habit %>%
  filter(species %in% phy$tip.label)

# Part a (left): tree
a <- ggtree(phy) %<+% filmy_habit +
  geom_tippoint(aes(color = habit), position = position_nudge(x = 7, y = 0), size = 4) +
  scale_color_manual(values = habit_colors, labels = pretty_text) +
  labs(color = "Growth habit")

>>>>

```{r combined-plot, fig.width = 6.85, fig.height = 5, fig.cap = ""}
# Copy data so they
# can be manipulated for this plot
phy <- filmy_phy
traits <- combined_species_means
habit <- filmy_habit

@@

# Filter growth habit data to only those in phylogeny
habit <-
  habit %>%
  filter(species %in% phy$tip.label)

# Part a (left): tree
a <- ggtree(phy) %<+% habit +
  geom_tippoint(aes(color = habit), position = position_nudge(x = 7, y = 0), size = 4) +
  scale_color_manual(values = habit_colors, labels = pretty_text) +
  labs(color = "Growth habit") +
  # There is no way modify the text in geom_treescale (to add units), so make the
  # text disappear by setting fontsize = 0
  geom_treescale(y = 12, x = 0, width = 40, fontsize = 0) +
  # Manually place custom label above scale bar
  annotate("text", x = 20, y = 12, label = "40 my", size = 2.5, vjust = -1)
